
\documentclass[12pt]{article}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}



\begin{document}



% Equations =======================================================================================
\section*{Equations}

\textbf{Total Impulse}
Thrust force integrated over the time of application.
\begin{equation}
    I_t = \int_{0}^{t}F\,dt 
\end{equation}

\bigskip
\noindent
\textbf{Specific Impulse:}
Thrust per unit propellant `weight' flow rate. 
\begin{equation}
    I_S = \frac{\int_{0}^{t}F\,dt }{g_0\int_{0}^{t}\dot{m}\,dt} = \frac{I_t}{w} 
\end{equation}

\bigskip
\noindent
\textbf{Total Propellant Weight:}
\begin{equation}
    w = m_p g_0
\end{equation}

\bigskip
\noindent
\textbf{Weight Flow Rate:}
\begin{equation}
    \dot{w} = \dot{m}_p g_0
\end{equation}

\bigskip
\noindent
\textbf{Effectice Exhaust Velocity:}
An average or mass-equivalent velocity at which propellant is being ejected from the nozzle.
\begin{equation}
    c = I_S g_0 = \frac{F}{\dot{m}} = v_2 + (p_2 - p_3) \frac{A_2}{\dot{m}}
\end{equation}

\bigskip
\noindent
\textbf{Characteristic Velocity:}
Compares relative performance of different chemical rocket propulsion systems. Essentially independent of nozzle characteristics. Can be related to the efficiency of the combustion process.
\begin{equation}
    c = I_S g_0 = \frac{F}{\dot{m}} = v_2 + (p_2 - p_3) \frac{A_2}{\dot{m}}
\end{equation}

\bigskip
\noindent
\textbf{Mass Ratio:}
Ratio of the final mass over the initial mass. 
\begin{equation}
    \mathbf{M}\mathbf{R} = \frac{m_f}{m_0}
\end{equation}

\bigskip
\noindent
\textbf{Propellant Mass Fractio:}
Ratio of the usefull propellant mass to the intitial mass.
\begin{equation}
    \mathbf{\zeta} = \frac{m_p}{m_0} = \frac{(m_0 - m_f)}{m_0} = \frac{m_p}{(m_p + m_f)}
\end{equation}

\bigskip
\noindent
\textbf{Impulse-to-Weight Ratio:}
The total impulse divided by the initial propellant-loaded vehicle sea-level weight.
\begin{equation}
    \frac{I_t}{w_o} = \frac{I_t}{(m_f + m_p) g_0} = \frac{I_S}{\frac{m_f}{m_p} + 1}
\end{equation}

\bigskip
\noindent
\textbf{Thrust:}
Momentum and pressure thrust.
\begin{equation}
    F = \dot{m} v_2 + (p_2 - p_3) A_2
\end{equation}



% Symbols =========================================================================================
\section*{Symbols}

\begin{tabbing}
\hspace{2cm} \= \hspace{7cm} \= \kill
    $I_t$                  \> Total Impulse                   \> N $\cdot$ s \\
    $I_S$                  \> Specific Impulse                \> s           \\
    $m_p$                  \> Total Effective Propellant Mass \> kg          \\
    $w$                    \> Effectice Propellant Weight     \> N           \\
    $\dot{m}$              \> Total Mass Flow Rate            \> kg / s      \\
    $\dot{w}$              \> Weight Flow Rate                \> N / s       \\
    $g_0$                  \> Earth's Average Gravity         \> kg / $s^2$  \\
    $c$                    \> Effectice Exhaust Velocity      \> m / s       \\
    $\mathbf{M}\mathbf{R}$ \> Mass Ratio                      \> Unitless    \\
    $m_f$                  \> Final Mass                      \> kg          \\
    $m_0$                  \> Initial Mass                    \> kg          \\
    $\zeta$                \> Propellant Mass Fraction        \> Unitless    \\
    $I_t$ / $w_0$          \> Impulse-to-Weight Ratio         \> s           \\
    $F$                    \> Thrust                          \> N           \\
    $v_2$                  \> Nozzle Exit Velocity            \> m / $s^2$   \\
    $p_2$                  \> Nozzle Exit Pressure            \> Pa          \\
    $p_3$                  \> Ambient Pressure                \> Pa          \\
    $A_2$                  \> Nozzle Exit Area                \> $m^2$       \\
    $c^*$                  \> Characteristic Velocity         \> m / s       \\
    $p_1$                  \> Chamber Pressure                \> Pa          \\
    $A_t$                  \> Throat Area                     \> $m^2$       \\
\end{tabbing}

\end{document}
